On the surprising effectiveness of a simple matrix exponential derivative approximation, with application to global SARS-CoV-2

### 2023-09-13 manuscript/pnas_revision.tex
more response

>>>>

\section{Visualizing the posterior mean random effects}

Figure

\begin{figure}[t]
	\centering
	\includegraphics[width=0.8\linewidth]{figures/randEffects.pdf}
	\caption{Posterior means for exponentiated random effects convey expected multiplicative deviations from the portion of the rate attributable to fixed effects for each corresponding element of the generator matrix.  Notably, we infer a roughly 1.8-fold posterior mean increase in the rate of transitions from the US to Hubei, CN, beyond that portion of the rate which may be explained by fixed effects.  Less pronounced are posterior mean multiplicative increases of 1.34 (US to Italy), 1.27 (US to UK), 1.44 (Netherlands to Italy) and 1.21 (Guangdong, CN, to Hubei, CN).}\label{fig:randEffs}
\end{figure}

### 2023-09-13 manuscript/revision_letter.tex
random effects imagwe
more response

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\linewidth]{figures/randEffects.pdf}
	\caption{Posterior means for exponentiated random effects convey expected multiplicative deviations from the portion of the rate attributable to fixed effects for each corresponding element of the generator matrix.  Notably, we infer a roughly 1.8-fold posterior mean increase in the rate of transitions from the US to Hubei, CN, beyond that portion of the rate which may be explained by fixed effects.  Less pronounced are posterior mean multiplicative increases of 1.34 (US to Italy), 1.27 (US to UK), 1.44 (Netherlands to Italy) and 1.21 (Guangdong, CN, to Hubei, CN).}
\end{figure}
